Variants of G\"{o}del's Ontological Proof \\ in a Natural Deduction Calculus

### 2016-09-16 Papers/InProgress/NaturalDeduction/GodProof-ND.tex
Replace brackets by parentheses

\begin{axiom}
\label{A1}
Either a property or its negation is positive, but not both:
$$
\all \varphi. [P(\neg \varphi) \biimp \neg P(\varphi)]
$$
\end{axiom}

\begin{axiom}
\label{A2}
A property necessarily implied by a positive property is positive:
$$
\all \varphi. \all \psi.[(P(\varphi) \wedge \nec \all x.[\varphi(x) \imp \psi(x)]) \imp P(\psi)]
$$
\end{axiom}

\begin{theorem}
\label{T1}
Positive properties are possibly exemplified:
$$
\all \varphi. [P(\varphi) \imp \pos \ex x.\varphi(x)]
$$
\end{theorem}
\begin{proof} \hfill

@@

\begin{small}
\begin{prooftree}
\AXC{$ $} \RightLabel{4}
\UIC{$\nec \neg \ex x. \rho(x)$} \RightLabel{$\nec_E$}
\UIC{$\omega: \neg \ex x. \rho(x)$}
        \AXC{$ $} \RightLabel{2}
        \UIC{$\omega: \rho(\alpha)$} \RightLabel{$\ex_I$}
		\UIC{$\omega: \ex x. \rho(x)$} \RightLabel{$\imp_E$}
    \BIC{$\omega: \bot$} \RightLabel{$\imp_I^2$}
	\UIC{$\omega: \neg \rho(\alpha)$} \RightLabel{$\all_I$}
	\UIC{$\omega: \all x. \neg \rho(x)$} \RightLabel{$\nec_I$}
	\UIC{$\nec \all x. \neg \rho(x) \scott$}
	        \AXC{$\subproof_3 $} \dashedLine
	        \UIC{$\bot$} \RightLabel{$\imp_I^3$}
    		\UIC{$\neg \nec \all x. \neg \rho(x)$} \RightLabel{$\imp_E$}
  		\BIC{$\bot$} \RightLabel{$\imp_I^4$}
  		\UIC{$ \neg \nec \neg \ex x.\rho(x)$} \doubleLine %\RightLabel{definition of $\pos$}
  		\UIC{$ \pos \ex x.\rho(x)$}  \RightLabel{$\imp_I^5$}
  		\UIC{$ P(\rho) \imp \pos \ex x.\rho(x)$} \RightLabel{$\all_I$}
      \UIC{$ \all \varphi. [P(\varphi) \imp \pos \ex x.\varphi(x)] $}
\end{prooftree}
\end{small}
\end{proof}

\begin{definition}
\label{D1}
A \emph{God-like} being possesses all positive properties:
$$
G(x) \equiv \forall \varphi. [P(\varphi) \to \varphi(x)]
$$
\end{definition}

@@

\begin{axiom}
\label{A4}
Positive properties are necessarily positive:
$$
\all \varphi.[P(\varphi) \to \Box \; P(\varphi)]
$$
\end{axiom}

@@

		\AXC{$ $} \RightLabel{1}
		\UIC{$\neg P(\rho)$} 
				\AXC{Axiom 1} \dashedLine
        \UIC{$\all \varphi. [P(\neg \varphi) \biimp \neg P(\varphi)]$} \RightLabel{$\all_E$}
        \UIC{$P(\lambda x. \neg \rho(x)) \biimp \neg P(\rho)$} \RightLabel{$\wedge_E$}
        \UIC{$\neg P(\rho) \imp P(\lambda x. \neg \rho(x))$} \RightLabel{$\imp_E$}
			\BIC{$P(\lambda x. \neg \rho(x))$}

@@

 \AXC{$\subproof_4$}\dashedLine
 \UIC{$P(\rho)$}
	      \AXC{Axiom 4} \dashedLine
        \UIC{$\all \varphi.[P(\varphi) \to \Box \; P(\varphi)]$} \RightLabel{$\all_E$}
	   	  \UIC{$P(\rho) \imp \nec P(\rho)$} \RightLabel{$\imp_E$}
		 \BIC{$\nec P(\rho)\scott$}
			\AXC{$ $} \RightLabel{3}
			\UIC{$\omega: P(\rho)$}
					\AXC{$ $} \RightLabel{2}
					\UIC{$\omega: G(\delta) $} \dottedLine
					\UIC{$\omega: \all \varphi. P(\varphi) \imp \varphi(\delta)$} \RightLabel{$\all_E$} 
					\UIC{$\omega: P(\rho) \imp \rho(\delta)$} \RightLabel{$\imp_E$}
				\BIC{$\omega: \rho(\delta) $} \RightLabel{$\imp_I^2$}
				\UIC{$\omega: G(\delta) \imp \rho(\delta) $} \RightLabel{$\all_I$}
				\UIC{$\omega: \all y. (G(y) \imp \rho(y)) $} \RightLabel{$\imp_I^3$}
				\UIC{$\omega: P(\rho) \imp \all y. (G(y) \imp \rho(y) )$} \RightLabel{$\nec_I$}
				\UIC{$\nec (P(\rho) \imp \all y. (G(y) \imp \rho(y) ))$} \doubleLine \RightLabel{Axiom K}

@@

\begin{definition}
\label{D3}
\emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
$$
E(x) \equiv \all \varphi.[\ess{\varphi}{x} \imp \nec \ex y.\varphi(y)]
$$
\end{definition}

@@

\begin{axiom}
\label{N:A1}
Either a property or its negation is positive, but not both:
$$
\all \varphi. [P(\neg \varphi) \biimp \neg P(\varphi)]
$$
\end{axiom}

\begin{axiom}
\label{N:A2}
A property necessarily implied by a positive property is positive:
$$
\all \varphi. \all \psi.[(P(\varphi) \wedge \nec \all x.[\varphi(x) \imp \psi(x)]) \imp P(\psi)]
$$
\end{axiom}
\begin{theorem}
\label{N:T1}
Positive properties are possibly exemplified:
$$
\all \varphi. [P(\varphi) \imp \pos \ex x.\varphi(x)]
$$
\end{theorem}
\begin{proof} \hfill

\begin{scriptsize}
\begin{prooftree}
\AXC{$ $} \RightLabel{3}
\UIC{$P(\rho)$} 
\AXC{$ $} \RightLabel{2}
\UIC{$\nec \neg \ex x.\rho(x) $} \RightLabel{$\nec_E$}
\UIC{$\omega: \neg \ex x.\rho(x) $} 
\AXC{$ $} \RightLabel{$1$}
\UIC{$\omega: \rho(x)$} \RightLabel{$\ex_I$}
\UIC{$\omega: \ex x.\rho(x) $} \RightLabel{$\imp_E$}
\BIC{$\omega:  \bot $}\RightLabel{$\imp_I^1$}
\UIC{$\omega:  \neg \rho(x) $} \RightLabel{$\imp_I$}
\UIC{$\omega:  \rho(x) \imp \neg \rho(x) $} \RightLabel{$\all_I$}
\UIC{$\omega:  \all x.(\rho(x) \imp \neg \rho(x)) $}  \RightLabel{$\nec_I$}
\UIC{$ \nec \all x.(\rho(x) \imp \neg \rho(x)) $}\RightLabel{$\wedge_I$}
\BIC{$ P(\rho) \wedge \nec \all x.[\rho(x) \imp \neg \rho(x)]$}
\AXC{Axiom \ref{A2} for $\rho$ and $\lambda x. \neg \rho(x)$} \dashedLine
\UIC{$(P(\rho) \wedge \nec \all x.[\rho(x) \imp \neg \rho(x)]) \imp P(\lambda x. \neg \rho(x))$} \RightLabel{$\imp_E$}
\BIC{$[\subproof_5]\qquad P(\lambda x. \neg \rho(x))$} \RightLabel{$\imp_E$}
\end{prooftree}
\end{scriptsize}

\begin{small}
\begin{prooftree}
\AXC{$\subproof_5$} \dashedLine
\UIC{$P(\lambda x. \neg \rho(x))$} \RightLabel{$\imp_E$}
\AXC{Axiom 1} \dashedLine
\UIC{$\all \varphi. [P(\neg \varphi) \biimp \neg P(\varphi)]$} \RightLabel{$\all_E$}
\UIC{$P(\lambda x. \neg \rho(x)) \biimp \neg P(\rho)$} \RightLabel{$\wedge_E$}
\UIC{$ P(\lambda x. \neg \rho(x)) \imp \neg P(\rho) $}  \RightLabel{$\imp_E$}
\BIC{$\neg P(\rho) $} 
\AXC{$ $} \RightLabel{3} 
\UIC{$P(\rho)$} \RightLabel{$\imp_E$}
\BIC{$\bot$} \RightLabel{$\imp_I^2$}
\UIC{$ \neg \nec \neg \ex x.\rho(x)$} \doubleLine %\RightLabel{definition of $\pos$}
\UIC{$ \pos \ex x.\rho(x)$}  \RightLabel{$\imp_I^3$}
\UIC{$ P(\rho) \imp \pos \ex x.\rho(x) $} \RightLabel{$\all_I$}
\UIC{$ \all \varphi. [P(\varphi) \imp \pos \ex x.\varphi(x)] $}

@@

\begin{definition}
\label{N:D1}
A \emph{God-like} being possesses all positive properties:
$$
G(x) \equiv \forall \varphi. [P(\varphi) \to \varphi(x)]
$$
\end{definition}

@@

\begin{axiom}
\label{N:A4}
Positive properties are necessarily positive:
$$
\all \varphi.[P(\varphi) \to \Box \; P(\varphi)]
$$
\end{axiom}

@@

\begin{definition}
\label{N:D3}
\emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
$$
E(x) \equiv \all \varphi.[\ess{\varphi}{x} \imp \nec \ex y.\varphi(y)]
$$
\end{definition}

@@

\begin{small}
\begin{prooftree}
\AXC{$ $} \RightLabel{2}
\UIC{$\neg P(\rho)$} 
\AXC{Axiom 1} \dashedLine
\UIC{$\all \varphi. [P(\neg \varphi) \biimp \neg P(\varphi)]$} \RightLabel{$\all_E$}
\UIC{$P(\lambda x. \neg \rho(x)) \biimp \neg P(\rho)$} \RightLabel{$\wedge_E$}
\UIC{$\neg P(\rho) \imp P(\lambda x. \neg \rho(x))$}\RightLabel{$\imp_E$}
\BIC{$P(\lambda x. \neg \rho(x))$}
\AXC{$ $} \RightLabel{1}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$G(\gamma)$}  \dottedLine \RightLabel{D\ref{N:D1}}
\UIC{$\forall \varphi.(P(\varphi) \imp \varphi(\gamma))$}\RightLabel{$\forall_E$}
\UIC{$P(\lambda x. \neg \rho(x)) \imp \neg \rho(\gamma)$}\RightLabel{$\imp_E$}
\BIC{$\neg \rho(\gamma)$}
\AXC{$ $} \RightLabel{3}
\UIC{$\rho(\gamma)$} \RightLabel{$\imp_E$}
\BIC{$\bot$}\RightLabel{$\imp_I^2$}
\UIC{$\neg\neg P(\rho)$}\RightLabel{$\neg\neg_E$}
\UIC{$[\subproof_6] \qquad P(\rho)$}
\end{prooftree}
\end{small}

@@

%\AXC{$ $} \RightLabel{6}
%\UIC{$\rho(\gamma)$} \RightLabel{}
\AXC{$ \subproof_6$} \dashedLine
\UIC{$P(\rho)$} %\RightLabel{$\nec_E$}
\AXC{Axiom \ref{N:A4}} \dashedLine
\UIC{$\all \varphi.[P(\varphi) \imp \nec\; P(\varphi)]$}\RightLabel{$\forall_E$}
\UIC{$P(\rho) \imp \nec\; P(\rho)$}\RightLabel{$\imp_E$}
\BIC{$\nec P(\rho)$}\RightLabel{$\imp_E$}%\RightLabel{$\imp_I^3$}
%\UIC{$[\subproof_7] \qquad \rho(\gamma) \imp \nec\; P(\rho)$}
%\UIC{$\rho(\gamma)\imp\Box P(\rho)$}\RightLabel{$\imp_E$}
%\BIC{$\nec P(\rho)$} \RightLabel{$\imp_E$}

@@

\begin{small}
\begin{prooftree}
\AXC{$\subproof_7$} \dashedLine
\UIC{$\ess{G}{\gamma}$}
\AXC{Axiom \ref{A5}} \dashedLine
\UIC{$P(E)$}\dottedLine 
\AXC{$ $} \RightLabel{1}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$G(\gamma)$}\dottedLine \RightLabel{D\ref{N:D1}}
\UIC{$\forall \varphi.(P(\varphi) \imp \varphi(\gamma))$}\RightLabel{$\forall_E$}
\UIC{$P(E) \imp E(\gamma)$}\RightLabel{$\imp_E$}
\BIC{$E(\gamma)$}\dottedLine \RightLabel{D\ref{N:D3}}
\UIC{$ \all \varphi.[\ess{\varphi}{\gamma} \imp \nec \ex x.\varphi(x)] $}\RightLabel{$\all_E$}
\UIC{$ \ess{G}{\gamma} \imp \nec \ex x. G(x) $}\RightLabel{$\imp_E$}
\BIC{$\nec \ex x. G(x)$} \RightLabel{$\imp_I^1$}
\UIC{$\ex z. G(z) \imp \nec \ex x. G(x)$}
\end{prooftree}
\end{small}
\end{proof}

@@

\begin{small}
\begin{prooftree}
\AXC{ Distribution Principle} \dashedLine
\UIC{$\nec [\ex x. G(x)\imp \nec \ex x. G(x)]\imp [\pos \ex x. G(x)\imp \pos\nec \ex x. G(x)]$}
\AXC{ Lemma \ref{N:L1} } \dashedLine
\UIC{$\ex x. G(x)\imp \nec \ex x. G(x)$}\RightLabel{$\nec_I$}
\UIC{$\nec[\ex x. G(x)\imp \nec \ex x. G(x)]$}\RightLabel{$\imp_E$}
\BIC{$\pos \ex x. G(x)\imp \pos\nec \ex x. G(x)$}
\end{prooftree}
\end{small}
\begin{small}
\begin{prooftree}
\AXC{$[\pos \ex x. G(x)\imp \pos\nec \ex x. G(x)]$}
\AXC{ Corollary \ref{C1} } \dashedLine
\UIC{$\pos \ex x. G(x)$}\RightLabel{$\imp_E$}
\BIC{$\pos\nec \ex x. G(x)$}
\AXC{ Brouwer's Reduction Principle } \dashedLine
\UIC{$\pos\nec \ex x. G(x) \imp \ex x. G(x)$}\RightLabel{$\imp_E$}
\BIC{$ \ex x. G(x)$} \RightLabel{$\nec_I$}
\UIC{$\nec \ex x. G(x)$} 
\end{prooftree}
\end{small}

@@

\begin{small}
\begin{prooftree}
\AXC{Theorem 2}\dashedLine
\UIC{$\all y.[G(y) \imp \ess{G}{y}]$} \RightLabel{D2 }\dottedLine
\UIC{$\all y.[G(y) \imp G(y) \wedge \all \psi. (\psi(y) \imp \nec \all x. (G(x) \imp \psi(x)))]$}\doubleLine
\UIC{$\all y.[G(y) \imp \all \psi. (\psi(y) \imp \nec \all x. (G(x) \imp \psi(x)))]$} \doubleLine
%\UIC{$\all y.[G(y) \imp (A(y) \imp \nec \all x. (G(x) \imp A(x)))]$} \RightLabel{$A$ is constant}
\UIC{$\all y.[G(y) \imp (A \imp \nec \all x. (G(x) \imp A))]$} \doubleLine
\UIC{$[\subproof_8] \qquad \ex y.G(y) \imp (A \imp \nec \all x. (G(x) \imp A))$}
\end{prooftree}
\end{small}

@@

%Anderson modification of the axioms in A1 equivalence removed and definition of essence altered. 
%Anderson's implication instead of equivalence. 
\begin{axiom}[Emended]
\label{A:A1}
If the negation of a property is positive, the property is not positive:
$$
\all \varphi. [P(\neg \varphi) \imp \neg P(\varphi)]
$$
\end{axiom}

\begin{axiom}[As in Scott's]
\label{A:A2}
A property necessarily implied by a positive property is positive:
$$
\all \varphi. \all \psi.[(P(\varphi) \wedge \nec \all x.[\varphi(x) \imp \psi(x)]) \imp P(\psi)]
$$
\end{axiom}

\begin{theorem}
\label{A:T1}
Positive properties are possibly exemplified:
$$
\all \varphi. [P(\varphi) \imp \pos \ex x.\varphi(x)]
$$
\end{theorem}
\begin{proof}
This proof is omitted, because any of the proofs of Theorem 1 in Sections \ref{sec:scott} and \ref{sec:newproof} would suffice to prove this theorem with only a small modification: the equivalence of axiom \ref{A1} would not need to be reduced to an implication by conjunction elimination. 
\end{proof}

\begin{definition}[Emended]
\label{A:D1}
A \emph{God-like} being necessarily possesses those and only those properties which are positive:
$$
G(x) \equiv \forall \varphi. [P(\varphi) \biimp \nec \varphi(x)]
$$
\end{definition}

@@

\begin{axiom}[As in Scott's]
\label{A:A4}
Positive properties are necessarily positive:
$$
\all \varphi.[P(\varphi) \to \Box \; P(\varphi)]
$$
\end{axiom}

@@

\begin{definition}[As in Scott's]
\label{A:D3}
\emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
$$
E(x) \equiv \all \varphi.[\ess{\varphi}{x} \imp \nec \ex y.\varphi(y)]
$$
\end{definition}

@@

\setcounter{definition}{0}
\begin{definition}[Changed]
\label{B:D1}
A property is \emph{positive} iff it is necessarily possessed by every God-like being.
$$
P_B(\varphi) \equiv \nec \all x. [G_B(x) \imp \varphi(x)]
$$
\end{definition}

>>>>

\begin{axiom}
\label{A1}
Either a property or its negation is positive, but not both:
$$
\all \varphi. (P(\neg \varphi) \biimp \neg P(\varphi))
$$
\end{axiom}

\begin{axiom}
\label{A2}
A property necessarily implied by a positive property is positive:
$$
\all \varphi. \all \psi.((P(\varphi) \wedge \nec \all x.(\varphi(x) \imp \psi(x))) \imp P(\psi))
$$
\end{axiom}

\begin{theorem}
\label{T1}
Positive properties are possibly exemplified:
$$
\all \varphi. (P(\varphi) \imp \pos \ex x.\varphi(x))
$$
\end{theorem}
\begin{proof} \hfill

@@

\begin{small}
\begin{prooftree}
\AXC{$ $} \RightLabel{4}
\UIC{$\nec \neg \ex x. \rho(x)$} \RightLabel{$\nec_E$}
\UIC{$\omega: \neg \ex x. \rho(x)$}
        \AXC{$ $} \RightLabel{2}
        \UIC{$\omega: \rho(\alpha)$} \RightLabel{$\ex_I$}
		\UIC{$\omega: \ex x. \rho(x)$} \RightLabel{$\imp_E$}
    \BIC{$\omega: \bot$} \RightLabel{$\imp_I^2$}
	\UIC{$\omega: \neg \rho(\alpha)$} \RightLabel{$\all_I$}
	\UIC{$\omega: \all x. \neg \rho(x)$} \RightLabel{$\nec_I$}
	\UIC{$\nec \all x. \neg \rho(x) \scott$}
	        \AXC{$\subproof_3 $} \dashedLine
	        \UIC{$\bot$} \RightLabel{$\imp_I^3$}
    		\UIC{$\neg \nec \all x. \neg \rho(x)$} \RightLabel{$\imp_E$}
  		\BIC{$\bot$} \RightLabel{$\imp_I^4$}
  		\UIC{$ \neg \nec \neg \ex x.\rho(x)$} \doubleLine %\RightLabel{definition of $\pos$}
  		\UIC{$ \pos \ex x.\rho(x)$}  \RightLabel{$\imp_I^5$}
  		\UIC{$ P(\rho) \imp \pos \ex x.\rho(x)$} \RightLabel{$\all_I$}
      \UIC{$ \all \varphi. (P(\varphi) \imp \pos \ex x.\varphi(x)) $}
\end{prooftree}
\end{small}
\end{proof}

\begin{definition}
\label{D1}
A \emph{God-like} being possesses all positive properties:
$$
G(x) \equiv \forall \varphi. (P(\varphi) \to \varphi(x))
$$
\end{definition}

@@

\begin{axiom}
\label{A4}
Positive properties are necessarily positive:
$$
\all \varphi.(P(\varphi) \to \Box \; P(\varphi))
$$
\end{axiom}

@@

		\AXC{$ $} \RightLabel{1}
		\UIC{$\neg P(\rho)$} 
				\AXC{Axiom 1} \dashedLine
        \UIC{$\all \varphi. (P(\neg \varphi) \biimp \neg P(\varphi))$} \RightLabel{$\all_E$}
        \UIC{$P(\lambda x. \neg \rho(x)) \biimp \neg P(\rho)$} \RightLabel{$\wedge_E$}
        \UIC{$\neg P(\rho) \imp P(\lambda x. \neg \rho(x))$} \RightLabel{$\imp_E$}
			\BIC{$P(\lambda x. \neg \rho(x))$}

@@

 \AXC{$\subproof_4$}\dashedLine
 \UIC{$P(\rho)$}
	      \AXC{Axiom 4} \dashedLine
        \UIC{$\all \varphi.(P(\varphi) \to \Box \; P(\varphi))$} \RightLabel{$\all_E$}
	   	  \UIC{$P(\rho) \imp \nec P(\rho)$} \RightLabel{$\imp_E$}
		 \BIC{$\nec P(\rho)\scott$}
			\AXC{$ $} \RightLabel{3}
			\UIC{$\omega: P(\rho)$}
					\AXC{$ $} \RightLabel{2}
					\UIC{$\omega: G(\delta) $} \dottedLine
					\UIC{$\omega: \all \varphi. P(\varphi) \imp \varphi(\delta)$} \RightLabel{$\all_E$} 
					\UIC{$\omega: P(\rho) \imp \rho(\delta)$} \RightLabel{$\imp_E$}
				\BIC{$\omega: \rho(\delta) $} \RightLabel{$\imp_I^2$}
				\UIC{$\omega: G(\delta) \imp \rho(\delta) $} \RightLabel{$\all_I$}
				\UIC{$\omega: \all y. (G(y) \imp \rho(y)) $} \RightLabel{$\imp_I^3$}
				\UIC{$\omega: P(\rho) \imp \all y. (G(y) \imp \rho(y) )$} \RightLabel{$\nec_I$}
				\UIC{$\nec (P(\rho) \imp \all y. (G(y) \imp \rho(y) ))$} \doubleLine \RightLabel{Axiom K}

@@

\begin{definition}
\label{D3}
\emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
$$
E(x) \equiv \all \varphi.(\ess{\varphi}{x} \imp \nec \ex y.\varphi(y))
$$
\end{definition}

@@

\begin{axiom}
\label{N:A1}
Either a property or its negation is positive, but not both:
$$
\all \varphi. (P(\neg \varphi) \biimp \neg P(\varphi))
$$
\end{axiom}

\begin{axiom}
\label{N:A2}
A property necessarily implied by a positive property is positive:
$$
\all \varphi. \all \psi.((P(\varphi) \wedge \nec \all x.(\varphi(x) \imp \psi(x))) \imp P(\psi))
$$
\end{axiom}
\begin{theorem}
\label{N:T1}
Positive properties are possibly exemplified:
$$
\all \varphi. (P(\varphi) \imp \pos \ex x.\varphi(x))
$$
\end{theorem}
\begin{proof} \hfill

\begin{scriptsize}
\begin{prooftree}
\AXC{$ $} \RightLabel{3}
\UIC{$P(\rho)$} 
\AXC{$ $} \RightLabel{2}
\UIC{$\nec \neg \ex x.\rho(x) $} \RightLabel{$\nec_E$}
\UIC{$\omega: \neg \ex x.\rho(x) $} 
\AXC{$ $} \RightLabel{$1$}
\UIC{$\omega: \rho(x)$} \RightLabel{$\ex_I$}
\UIC{$\omega: \ex x.\rho(x) $} \RightLabel{$\imp_E$}
\BIC{$\omega:  \bot $}\RightLabel{$\imp_I^1$}
\UIC{$\omega:  \neg \rho(x) $} \RightLabel{$\imp_I$}
\UIC{$\omega:  \rho(x) \imp \neg \rho(x) $} \RightLabel{$\all_I$}
\UIC{$\omega:  \all x.(\rho(x) \imp \neg \rho(x)) $}  \RightLabel{$\nec_I$}
\UIC{$ \nec \all x.(\rho(x) \imp \neg \rho(x)) $}\RightLabel{$\wedge_I$}
\BIC{$ P(\rho) \wedge \nec \all x.(\rho(x) \imp \neg \rho(x))$}
\AXC{Axiom \ref{A2} for $\rho$ and $\lambda x. \neg \rho(x)$} \dashedLine
\UIC{$(P(\rho) \wedge \nec \all x.(\rho(x) \imp \neg \rho(x))) \imp P(\lambda x. \neg \rho(x))$} \RightLabel{$\imp_E$}
\BIC{$[\subproof_5]\qquad P(\lambda x. \neg \rho(x))$} \RightLabel{$\imp_E$}
\end{prooftree}
\end{scriptsize}

\begin{small}
\begin{prooftree}
\AXC{$\subproof_5$} \dashedLine
\UIC{$P(\lambda x. \neg \rho(x))$} \RightLabel{$\imp_E$}
\AXC{Axiom 1} \dashedLine
\UIC{$\all \varphi. (P(\neg \varphi) \biimp \neg P(\varphi))$} \RightLabel{$\all_E$}
\UIC{$P(\lambda x. \neg \rho(x)) \biimp \neg P(\rho)$} \RightLabel{$\wedge_E$}
\UIC{$ P(\lambda x. \neg \rho(x)) \imp \neg P(\rho) $}  \RightLabel{$\imp_E$}
\BIC{$\neg P(\rho) $} 
\AXC{$ $} \RightLabel{3} 
\UIC{$P(\rho)$} \RightLabel{$\imp_E$}
\BIC{$\bot$} \RightLabel{$\imp_I^2$}
\UIC{$ \neg \nec \neg \ex x.\rho(x)$} \doubleLine %\RightLabel{definition of $\pos$}
\UIC{$ \pos \ex x.\rho(x)$}  \RightLabel{$\imp_I^3$}
\UIC{$ P(\rho) \imp \pos \ex x.\rho(x) $} \RightLabel{$\all_I$}
\UIC{$ \all \varphi. (P(\varphi) \imp \pos \ex x.\varphi(x)) $}

@@

\begin{definition}
\label{N:D1}
A \emph{God-like} being possesses all positive properties:
$$
G(x) \equiv \forall \varphi. (P(\varphi) \to \varphi(x))
$$
\end{definition}

@@

\begin{axiom}
\label{N:A4}
Positive properties are necessarily positive:
$$
\all \varphi.(P(\varphi) \to \Box \; P(\varphi))
$$
\end{axiom}

@@

\begin{definition}
\label{N:D3}
\emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
$$
E(x) \equiv \all \varphi.(\ess{\varphi}{x} \imp \nec \ex y.\varphi(y))
$$
\end{definition}

@@

\begin{small}
\begin{prooftree}
\AXC{$ $} \RightLabel{2}
\UIC{$\neg P(\rho)$} 
\AXC{Axiom 1} \dashedLine
\UIC{$\all \varphi. (P(\neg \varphi) \biimp \neg P(\varphi))$} \RightLabel{$\all_E$}
\UIC{$P(\lambda x. \neg \rho(x)) \biimp \neg P(\rho)$} \RightLabel{$\wedge_E$}
\UIC{$\neg P(\rho) \imp P(\lambda x. \neg \rho(x))$}\RightLabel{$\imp_E$}
\BIC{$P(\lambda x. \neg \rho(x))$}
\AXC{$ $} \RightLabel{1}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$G(\gamma)$}  \dottedLine \RightLabel{D\ref{N:D1}}
\UIC{$\forall \varphi.(P(\varphi) \imp \varphi(\gamma))$}\RightLabel{$\forall_E$}
\UIC{$P(\lambda x. \neg \rho(x)) \imp \neg \rho(\gamma)$}\RightLabel{$\imp_E$}
\BIC{$\neg \rho(\gamma)$}
\AXC{$ $} \RightLabel{3}
\UIC{$\rho(\gamma)$} \RightLabel{$\imp_E$}
\BIC{$\bot$}\RightLabel{$\imp_I^2$}
\UIC{$\neg\neg P(\rho)$}\RightLabel{$\neg\neg_E$}
\UIC{$[\subproof_6] \qquad P(\rho)$}
\end{prooftree}
\end{small}

@@

%\AXC{$ $} \RightLabel{6}
%\UIC{$\rho(\gamma)$} \RightLabel{}
\AXC{$ \subproof_6$} \dashedLine
\UIC{$P(\rho)$} %\RightLabel{$\nec_E$}
\AXC{Axiom \ref{N:A4}} \dashedLine
\UIC{$\all \varphi.(P(\varphi) \imp \nec\; P(\varphi))$}\RightLabel{$\forall_E$}
\UIC{$P(\rho) \imp \nec\; P(\rho)$}\RightLabel{$\imp_E$}
\BIC{$\nec P(\rho)$}\RightLabel{$\imp_E$}%\RightLabel{$\imp_I^3$}
%\UIC{$[\subproof_7] \qquad \rho(\gamma) \imp \nec\; P(\rho)$}
%\UIC{$\rho(\gamma)\imp\Box P(\rho)$}\RightLabel{$\imp_E$}
%\BIC{$\nec P(\rho)$} \RightLabel{$\imp_E$}

@@

\begin{small}
\begin{prooftree}
\AXC{$\subproof_7$} \dashedLine
\UIC{$\ess{G}{\gamma}$}
\AXC{Axiom \ref{A5}} \dashedLine
\UIC{$P(E)$}\dottedLine 
\AXC{$ $} \RightLabel{1}
\UIC{$\ex z. G(z)$}\RightLabel{$\ex_E$}
\UIC{$G(\gamma)$}\dottedLine \RightLabel{D\ref{N:D1}}
\UIC{$\forall \varphi.(P(\varphi) \imp \varphi(\gamma))$}\RightLabel{$\forall_E$}
\UIC{$P(E) \imp E(\gamma)$}\RightLabel{$\imp_E$}
\BIC{$E(\gamma)$}\dottedLine \RightLabel{D\ref{N:D3}}
\UIC{$ \all \varphi.(\ess{\varphi}{\gamma} \imp \nec \ex x.\varphi(x)) $}\RightLabel{$\all_E$}
\UIC{$ \ess{G}{\gamma} \imp \nec \ex x. G(x) $}\RightLabel{$\imp_E$}
\BIC{$\nec \ex x. G(x)$} \RightLabel{$\imp_I^1$}
\UIC{$\ex z. G(z) \imp \nec \ex x. G(x)$}
\end{prooftree}
\end{small}
\end{proof}

@@

\begin{small}
\begin{prooftree}
\AXC{ Distribution Principle} \dashedLine
\UIC{$\nec (\ex x. G(x)\imp \nec \ex x. G(x)) \imp (\pos \ex x. G(x)\imp \pos\nec \ex x. G(x))$}
\AXC{ Lemma \ref{N:L1} } \dashedLine
\UIC{$\ex x. G(x)\imp \nec \ex x. G(x)$}\RightLabel{$\nec_I$}
\UIC{$\nec(\ex x. G(x)\imp \nec \ex x. G(x))$}\RightLabel{$\imp_E$}
\BIC{$\pos \ex x. G(x)\imp \pos\nec \ex x. G(x)$}
\end{prooftree}
\end{small}
\begin{small}
\begin{prooftree}
\AXC{$\pos \ex x. G(x)\imp \pos\nec \ex x. G(x)$}
\AXC{ Corollary \ref{C1} } \dashedLine
\UIC{$\pos \ex x. G(x)$}\RightLabel{$\imp_E$}
\BIC{$\pos\nec \ex x. G(x)$}
\AXC{ Brouwer's Reduction Principle } \dashedLine
\UIC{$\pos\nec \ex x. G(x) \imp \ex x. G(x)$}\RightLabel{$\imp_E$}
\BIC{$ \ex x. G(x)$} \RightLabel{$\nec_I$}
\UIC{$\nec \ex x. G(x)$} 
\end{prooftree}
\end{small}

@@

\begin{small}
\begin{prooftree}
\AXC{Theorem 2}\dashedLine
\UIC{$\all y.(G(y) \imp \ess{G}{y})$} \RightLabel{D2 }\dottedLine
\UIC{$\all y.(G(y) \imp G(y) \wedge \all \psi. (\psi(y) \imp \nec \all x. (G(x) \imp \psi(x))))$}\doubleLine
\UIC{$\all y.(G(y) \imp \all \psi. (\psi(y) \imp \nec \all x. (G(x) \imp \psi(x))))$} \doubleLine
%\UIC{$\all y.(G(y) \imp (A(y) \imp \nec \all x. (G(x) \imp A(x))))$} \RightLabel{$A$ is constant}
\UIC{$\all y.(G(y) \imp (A \imp \nec \all x. (G(x) \imp A)))$} \doubleLine
\UIC{$[\subproof_8] \qquad \ex y.G(y) \imp (A \imp \nec \all x. (G(x) \imp A))$}
\end{prooftree}
\end{small}

@@

%Anderson modification of the axioms in A1 equivalence removed and definition of essence altered. 
%Anderson's implication instead of equivalence. 
\begin{axiom}[Emended]
\label{A:A1}
If the negation of a property is positive, the property is not positive:
$$
\all \varphi. (P(\neg \varphi) \imp \neg P(\varphi))
$$
\end{axiom}

\begin{axiom}[As in Scott's]
\label{A:A2}
A property necessarily implied by a positive property is positive:
$$
\all \varphi. \all \psi.((P(\varphi) \wedge \nec \all x.(\varphi(x) \imp \psi(x))) \imp P(\psi))
$$
\end{axiom}

\begin{theorem}
\label{A:T1}
Positive properties are possibly exemplified:
$$
\all \varphi. (P(\varphi) \imp \pos \ex x.\varphi(x))
$$
\end{theorem}
\begin{proof}
This proof is omitted, because any of the proofs of Theorem 1 in Sections \ref{sec:scott} and \ref{sec:newproof} would suffice to prove this theorem with only a small modification: the equivalence of axiom \ref{A1} would not need to be reduced to an implication by conjunction elimination. 
\end{proof}

\begin{definition}[Emended]
\label{A:D1}
A \emph{God-like} being necessarily possesses those and only those properties which are positive:
$$
G(x) \equiv \forall \varphi. (P(\varphi) \biimp \nec \varphi(x))
$$
\end{definition}

@@

\begin{axiom}[As in Scott's]
\label{A:A4}
Positive properties are necessarily positive:
$$
\all \varphi.(P(\varphi) \to \Box \; P(\varphi))
$$
\end{axiom}

@@

\begin{definition}[As in Scott's]
\label{A:D3}
\emph{Necessary existence} of an individual is the necessary exemplification of all its essences:
$$
E(x) \equiv \all \varphi.(\ess{\varphi}{x} \imp \nec \ex y.\varphi(y))
$$
\end{definition}

@@

\setcounter{definition}{0}
\begin{definition}[Changed]
\label{B:D1}
A property is \emph{positive} iff it is necessarily possessed by every God-like being.
$$
P_B(\varphi) \equiv \nec \all x. (G_B(x) \imp \varphi(x))
$$
\end{definition}
